Treefelling_Sylvain's version

### 2021-07-29 R/DraftFunctions.Rmd
Treefelling functions

```{r}
library(Maria)
library(readr)
library(dplyr)
library(tibble)
library(tidyr)
library(schoolmath)
library(ggplot2)
library(reshape)
library(sf)
```

>>>>

```{r}
library(Maria)
library(readr)
library(dplyr)
library(tibble)
library(tidyr)
library(schoolmath)
library(ggplot2)
library(reshape)
library(sf)
library(nngeo)
library(raster)
library(topoDistance)
library(BIOMASS)
```

### 2021-07-29 R/Treefelling_Sylvain's version.Rmd
Treefelling functions

```{r}
dat <- SelectedTrees[1,]
st_tree <- function(dat,
                    ScndTrail = ScndTrail,
                    MainTrail = MainTrail,
                    fuel, 
                    directionalfelling, 
                    advancedloggingparameters = loggingparameters()){

@@

# Marche pas encore
FellingTrees <- inventory %>% 
  group_by(idTree) %>% # for each tree and each given angle 
  do(geometry =  # inform geometry. # Filling a column from a function whose input is a table
       ifelse(!is.na(.$TreeFellingOrientationSuccess),
              st_tree(.,
                      ScndTrail = ScndTrail,
                      MainTrail = MainTrail,
                      fuel = "2", directionalfelling ="2",
                      advancedloggingparameters = loggingparameters())$A,
              NULL)) %>%
  mutate(geometry = as(geometry, "sfc_MULTIPOLYGON")) %>% # list -> sfc_MULTIPOLYGON
  st_as_sf()

@@

ggplot() +
  # geom_sf(data = Foot) +
  geom_sf(data = Trail) +
  geom_sf(data = NearestPoints) +
  # geom_sf(data = TrailPt) +
  geom_sf(data = FellingTrees)
```

```{r}
st_tree(SelectedTrees[1,],
        ScndTrail = ScndTrail,
        MainTrail = MainTrail,
        fuel = "2", directionalfelling ="2",
        advancedloggingparameters = loggingparameters())$A

FellingTrees <- inventory %>%
  group_by(idTree) %>% 
  mutate(geometry =
           ifelse(!is.na(TreeFellingOrientationSuccess),
                  "A", "B"))

FellingTrees <- inventory %>%
  group_by(idTree) %>% 
  do(geometry =
       ifelse(!is.na(.$TreeFellingOrientationSuccess),
              tolower("A"), "B"))

FellingTrees <- inventory %>% 
  group_by(idTree) %>% # for each tree and each given angle 
  do(geometry =  # inform geometry. # Filling a column from a function whose input is a table
       ifelse(!is.na(.$TreeFellingOrientationSuccess),
              st_tree(.,
                      ScndTrail = ScndTrail,
                      MainTrail = MainTrail,
                      fuel = "2", directionalfelling ="2",
                      advancedloggingparameters = loggingparameters())$A,
              NULL)) %>%
  mutate(geometry = as(geometry, "sfc_MULTIPOLYGON")) %>% # list -> sfc_MULTIPOLYGON
  st_as_sf()

felttress <- NA
inventory %>% 
  filter(!is.na(TreeFellingOrientationSuccess)) %>% 
  group_by(idTree) %>% # for each tree and each given angle 
  do(geometry =  # inform geometry. # Filling a column from a function whose input is a table
       st_tree(.,
               ScndTrail = ScndTrail,
               MainTrail = MainTrail,
               fuel = "2", directionalfelling = "2",
               advancedloggingparameters = loggingparameters())$A) %>%
  mutate(geometry = as(geometry, "sfc_MULTIPOLYGON")) %>% # list -> sfc_MULTIPOLYGON
  st_as_sf() %>% 
  mutate(geometry = st_as_text(geometry))

left_join(inventory, poly) %>% 
  ggplot() +
  geom_sf()

?sf
st_as_text(poly$geometry)

felttrees <- inventory %>% 
  filter(!is.na(TreeFellingOrientationSuccess)) %>% 
  group_by(idTree) %>% 
  do(treepolygon = 
       st_tree(.,
               ScndTrail = ScndTrail,
               MainTrail = MainTrail,
               fuel = "2", directionalfelling = "2",
               advancedloggingparameters = loggingparameters())$A %>% 
       st_as_text()) %>% 
  unnest(treepolygon)

inventory2 <- left_join(inventory, felttrees)

get_treepolygon <- function(inventory){
  inventory %>% 
    filter(!is.na(treepolygon)) %>%
    st_as_sf(wkt = "treepolygon")
}

ggplot() +
  geom_sf(data = st_as_sf(inventory, coords = c("Xutm", "Yutm"))) +
  geom_sf(data = get_treepolygon(inventory2), fill = "red")

st_intersection(
  get_treepolygon(inventory2),
  st_as_sf(inventory, coords = c("Xutm", "Yutm"))
) %>% 
  ggplot() +
  geom_sf()
```

>>>>

```{r}
st_tree <- function(dat,
                    ScndTrail = ScndTrail,
                    MainTrail = MainTrail,
                    fuel, 
                    directionalfelling, 
                    advancedloggingparameters = loggingparameters()){

@@

@@

ggplot() +
  # geom_sf(data = Foot) +
  geom_sf(data = ScndTrail) +
  geom_sf(data = MainTrail) +
  geom_sf(data = NearestPoints) +
  # geom_sf(data = TrailPt) +
  geom_sf(data = FellingTrees)
```

```{r}

felttress <- NA

# poly <- inventory %>% 
#   filter(!is.na(TreeFellingOrientationSuccess)) %>% 
#   group_by(idTree) %>% # for each tree 
#   do(geometry =  # inform geometry. # Filling a column from a function whose input is a table
#        st_tree(.,
#                ScndTrail = ScndTrail,
#                MainTrail = MainTrail,
#                fuel = "2", directionalfelling = "2",
#                advancedloggingparameters = loggingparameters())$A) %>%
#   mutate(geometry = as(geometry, "sfc_MULTIPOLYGON")) %>% # list -> sfc_MULTIPOLYGON
#   st_as_sf() %>% 
#   mutate(geometry = st_as_text(geometry)) # as text to easy join with a non spacial table
# 
# 
# left_join(inventory, poly) %>% 
#   ggplot() +
#   geom_sf()
# 
# st_as_text(poly$geometry)

felttrees <- inventory %>% 
  filter(!is.na(TreeFellingOrientationSuccess)) %>% 
  group_by(idTree) %>% # for each tree
  do(treepolygon = # inform geometry. # Filling a column from a function whose input is a table
       st_tree(.,
               ScndTrail = ScndTrail,
               MainTrail = MainTrail,
               fuel = "2", directionalfelling = "2",
               advancedloggingparameters = loggingparameters())$A %>% 
       st_as_text())  # as text to easy join with a non spacial table
  # unnest(treepolygon) # display the small dataframe in the big dataframe in one

inventory <- left_join(inventory, felttrees) # join spatial filtered inventory and non spatial complete inventory

get_treepolygon <- function(inventory){ # function from text (wkt) to sf
  inventory %>% 
    filter(!is.na(treepolygon)) %>%
    st_as_sf(wkt = "treepolygon")
}

ggplot() +
  geom_sf(data = st_as_sf(inventory, coords = c("Xutm", "Yutm"))) + # all the individuals of the plot
  geom_sf(data = get_treepolygon(inventory), fill = "red") # trees polygons

st_intersection( # trees under the fallen trees
  get_treepolygon(inventory),
  st_as_sf(inventory, coords = c("Xutm", "Yutm"))
) %>% 
  ggplot() +
  geom_sf()
```
